---
title: "KNN_NETSHOW"
author: "Whitney Chu"
date: "24/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#import data
```{r}
library(datasets)
library(class)
library(tidyr)
library(tidyverse)    
library(e1071)  
library(RColorBrewer)
library(dplyr)
library(caTools)
library(reshape2)
library(ggplot2)
library(stringr)
library(DMwR)
library(mltools)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(caret)
library(ggcorrplot)
```

#Read and import data
```{r}
data <- read.csv("ALL_COUNTRIES.csv")
data
```

#Preview the Dataset
```{r}
set.seed(100)
data <- data[sample(nrow(data), 2500),]
data <- data[,c(2,7,10)]
data
head(data)
summary(data)
dim(data)
str(data)
```

#check for missing data
```{r}
colSums(is.na(data))
```

#convert categorical variables
```{r}
data$show_type <- as.numeric(as.factor(data$show_type))
data$is_NF_Ori <- as.numeric(as.factor(data$is_NF_Ori))
str(data)
```

#split into training and testing set 
```{r}
nrow(data)
rows <- c(1:nrow(data))
split <- sample(rows,size = (nrow(data)*0.80))
train <- as.data.frame(data[split,])
test <- as.data.frame(data[-split,])

nrow(train)
head(train)
nrow(test)
head(test)
```

#build the KNN network
```{r}
# Empty variables
pred <- list()
accuracy <- numeric()

# From k=1 to k=100...
for(k in 1:100){
  
  # KnnTestPrediction for each k
  pred[[k]] <- knn(train[,1:2], test[,1:2], train$imdb_rating, k, prob=TRUE)
  
  # Accuracy for each k   
  accuracy[k] <- sum(pred[[k]]==test$imdb_rating)/length(test$imdb_rating)*100
  print(cat(as.character(k) , as.character(accuracy[k])))
}

#find optimal k
index<-which(accuracy %in% max(accuracy))
index<-index[1]
index

# Accuracy vs Choice of k
?plot
plot(accuracy, type="b", col="dodgerblue", 
     xlab="k, number of neighbors", ylab="Classification accuracy", 
     main="Accuracy vs Neighbors")

# Add lines indicating k with best accuracy
abline(v=which(accuracy==max(accuracy)), col="orange", lwd=1.5)

# Add line for max accuracy seen
?abline
abline(h=max(accuracy), col="red", lty=2)
# lty=2 for dashed

# Add line for min accuracy seen 
abline(h=min(accuracy), col="grey", lty=2)

k <- knn(train = train[,1:2], test = test[,1:2], cl = train$imdb_rating, k=index)
k <- as.data.frame(k)
```

#predict and get error
```{r}
test <- as.data.frame(test)

#pred <- predict(k1, test[,7])
pred<-as.numeric(as.numeric(as.character(sub("," , ".", unlist(k)))))

results2<- data.frame(actual = test$imdb_rating, prediction = pred)
results2
paste("RMSE =",RMSE(test$imdb_rating, pred))
```

#Print first row
```{r}
newtest<- test[1,1:2]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(data$show_type))){
  for (j in 1:as.numeric(max(data$is_NF_Ori))){
      newtest[nrow(newtest) + 1,] = list(q,j)
  }
}
```

#predict and order results in descending order
```{r}
k1 <- knn(train = train[,1:2], test = newtest[,1:2], cl = train$imdb_rating, k=1)
k1 <- as.data.frame(k1)
k1<- as.data.frame(k1)
test <- as.data.frame(test)
index[1]

#pred <- predict(k1, test[,7])
pred<-as.numeric(as.numeric(as.character(sub("," , ".", unlist(k1)))))

a<-data.frame(newtest[,1:3],pred)
a
qw<- a[order(a$pred,decreasing = TRUE),][-1,]
qw
```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  STnum <- as.numeric(row$show_type[1])
  NOnum <- as.numeric(row$is_NF_Ori[1])
  
  #look in show type in factored movie data table
  #store the index number
  #look back at show type in original data table
  #print out character genre for that index
  index<-data[which(data[,"show_type"]==STnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  STLabel <- data1[index,1]
  
  #look in is_NF_Ori in factored movie data table
  index<-data[which(data[,"is_NF_Ori"]==NOnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  NOLabel <- data1[index,2]
  
    #returns top combination into a list
  return <- list(STLabel,NOLabel)
}
```

#Top 3 combinations of movie genres
```{r}
topLabels<- test[1,1:2]
topLabels
for (i in 1:3){
  labels<- getStringGenres(qw[i,])
  topLabels[nrow(topLabels) + 1,] = labels
  if(i==1){
    topLabels<-topLabels[-1,]
  }
}
#top 3 
topLabels

