---
title: "LOG.R-NETSHOW"
author: "Whitney Chu"
date: "01/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Import libraries
```{r}
library(caret)
library(forecast)
library(tidyverse)    
library(e1071)  
library(RColorBrewer)
library(dplyr)
library(caTools)
library(pROC)
```

#Read and Import Data
```{r}
data <- read.csv("ALL_COUNTRIES.csv")
data
```

#Preview the Dataset
```{r}
set.seed(100)
data <- data[sample(nrow(data), 2500),]
data <- data[,c(2,7,10)]
data
head(data)
summary(data)
dim(data)
str(data)

data1<- data
```

#check for missing data
```{r}
colSums(is.na(data))
```

# Adding binary, dependent variable for logistic regression analysis
```{r}
data$FavourableMovie <- ifelse(data$imdb_rating>=0.64,1,0)
str(data)
View(data)
```

#convert categorical variables
```{r}
data$show_type <- as.numeric(as.factor(data$show_type))
data$is_NF_Ori <- as.numeric(as.factor(data$is_NF_Ori))
str(data)
```


#split into training and testing set 
```{r}
nrow(data)
rows <- c(1:nrow(data))
split <- sample(rows,size = (nrow(data)*0.80))
train <- as.data.frame(data[split,])
test <- as.data.frame(data[-split,])
nrow(train)
head(train)
nrow(test)
head(test)
```

#Create Logistic Regression model 
```{r}
LOG.REG1 <- glm(formula = FavourableMovie ~ show_type + is_NF_Ori, data = train, family= "binomial")
summary(LOG.REG1)
```


#validate the linear regression model
```{r}
train.control <- trainControl(method = "cv", number = 5)
model <- train(FavourableMovie ~ show_type + is_NF_Ori, data = train, method = "glm", trControl = train.control)
print(model)
```

# Assessing the Testing error 
```{r}
predict.ret1 <- predict(LOG.REG1,test)
pred <- ifelse(predict.ret1 >=0.64, "1", "0")
mean(test$FavourableMovie!=pred)
table(pred, test$FavourableMovie)
```

#ROC curve
```{r}
plot(roc(test$FavourableMovie, predict.ret1, direction="<"),
     col="yellow", lwd=3, main="ROC curve")
```

#Evaluating a cut-off value 
```{r}
X <- c(seq(0,1,0.01))
ErrorVector <- c(0:100)
Y=0
for(cut in X)
{
 LOG.Train.Prediction <- LOG.REG1$fitted>cut
 LogitTrainError <- mean(LOG.Train.Prediction!=train$FavourableMovie)
 Y=Y+1
 ErrorVector[Y] <- LogitTrainError
  
}
summary(ErrorVector)
plot(X,ErrorVector,main='Error versus cut')
```

#Print first row
```{r}
newtest<- test[1,1:2]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(data$show_type))){
  for (j in 1:as.numeric(max(data$is_NF_Ori))){
      newtest[nrow(newtest) + 1,] = list(q,j)
  }
}
```

#predict and order results in descending order
```{r}
predict.ret <- predict(LOG.REG1,newtest[,1:2])
predict.ret <- as.data.frame(predict.ret)
predict.ret1 <- predict.ret

#binary result - inconclusive
pred <- ifelse(predict.ret>=0.64, "1", "0")
a <- data.frame(newtest[,1:2],pred)
a
qw <- a[order(a$predict.ret,decreasing = TRUE),][-1,]
qw

#without making prediction binary
a2 <- data.frame(newtest[,1:2],predict.ret1)
a2
qw2 <- a2[order(a2$predict.ret,decreasing = TRUE),][-1,]
qw2

```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  STnum <- as.numeric(row$show_type[1])
  NOnum <- as.numeric(row$is_NF_Ori[1])

  #look in show type in factored movie data table
  #store the index number
  #look back at genre 1 in original data table
  #print out character genre for that index
  index<-data[which(data[,"show_type"]==STnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  STLabel <- data1[index,1]
  
  #look in genre 2 in factored movie data table
  index<-data[which(data[,"is_NF_Ori"]==NOnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  NOLabel <- data1[index,2]
  
  #returns three genres into a list
  return <- list(STLabel,NOLabel)
}
```

#Top 3 combinations of movie genres
```{r}
topLabels<- test[1,1:2]

for (i in 1:3){
  labels <- getStringGenres(qw2[i,])
  topLabels[nrow(topLabels) + 1,] = labels
}
#top 3
topLabels[-1,]
```

