---
title: "LR_GENRES"
author: "Whitney Chu"
date: "04/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import libraries
```{r}
library(forecast)
library(tidyverse)    
library(e1071)  
library(RColorBrewer)
library(dplyr)
library(caTools)
```

#Read and Import Data
```{r}
movie.data <- read.csv("IMDb_movies.csv")
movie.data
```

#Preview the Dataset
```{r}
set.seed(100)
movie.data <- movie.data[sample(nrow(movie.data), 2500),]
movie.data <- movie.data[,c(6:8,14)]
movie.data
head(movie.data)
summary(movie.data)
dim(movie.data)
str(movie.data)

movie.data1 <- movie.data
```

#check for missing data
```{r}
colSums(is.na(movie.data))
```

#convert categorical variables
```{r}
movie.data$genre1 <- as.numeric(as.factor(movie.data$genre1))
movie.data$genre2 <- as.numeric(as.factor(movie.data$genre2))
movie.data$genre3 <- as.numeric(as.factor(movie.data$genre3))
movie.data
```

#split into training and testing set 
```{r}
nrow(movie.data)
rows <- c(1:nrow(movie.data))
split <- sample(rows,size = (nrow(movie.data)*0.80))
train1 <- as.data.frame(movie.data[split,])
test1 <- as.data.frame(movie.data[-split,])
nrow(train1)
head(train1)
str(train1)
nrow(test1)
head(test1)
```

#create Linerar Regression model 
```{r}
lr <- lm(avg_vote ~ ., data = train1)
summary(lr)
plot(lr$residuals, pch = 16, col = "blue") #Plot the results
```

#validate the linear regression model
```{r}
train.control <- trainControl(method = "cv", number = 5)
model <- train(avg_vote ~ ., data = train1, method = "lm", trControl = train.control)
print(model)
```

#predict on lr 
```{r}
pred <- predict(lr, data.frame(test1))

pred <- round(pred, digits = 1)
#error
paste( "RMSE =",RMSE(test1$avg_vote, pred))

#residuals
Residuals <- test1$avg_vote - pred
data.frame("Predicted" = pred, "Actual" = test1$avg_vote,"Residual" = Residuals )
hist(Residuals, breaks = 25, xlab = "Residuals", main = "")
```

#Print first row
```{r}
newtest<- test1[1,1:3]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(movie.data$genre1))){
  for (j in 1:as.numeric(max(movie.data$genre2))){
    for (x in 1:as.numeric(max(movie.data$genre3))){
      newtest[nrow(newtest) + 1,] = list(q,j,x)
    }
  }
}
```

#predict and order results in descending order
```{r}
pred <- predict(lr, data.frame(newtest[,1:3]))
pred<-as.data.frame(pred)
a<-data.frame(newtest[,1:3],pred$pred)
a
qw<-a[order(a$pred.pred,decreasing = TRUE),][-1,]
qw
```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  g1num <- as.numeric(row$genre1[1])
  g2num <- as.numeric(row$genre2[1])
  g3num <- as.numeric(row$genre3[1])
  
  #look in genre 1 in factored movie data table
  #store the index number
  #look back at genre 1 in original data table
  #print out character genre for that index
    index<-movie.data[which(movie.data[,"genre1"]==g1num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g1Label <- movie.data1[index,1]
  
  #look in genre 2 in factored movie data table
  index<-movie.data[which(movie.data[,"genre2"]==g2num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g2Label <- movie.data1[index,2]
  
  #look in genre 3 in factored movie data table
  index<-movie.data[which(movie.data[,"genre3"]==g3num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g3Label <- movie.data1[index,3]
  
  #returns three genres into a list
  return <- list(g1Label,g2Label,g3Label)
}
```

#Top 10 combinations of movie genres
```{r}
topLabels<- test1[1,1:3]

for (i in 1:20){
  labels<- getStringGenres(qw[i,])
  topLabels[nrow(topLabels) + 1,] = labels
}
#top 10 
topLabels[-1,]
```