---
title: "LR_NETO"
author: "Whitney Chu"
date: "22/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import libraries
```{r}
library(datasets)
library(neuralnet)
library(caret)
library(reshape2)
library(ggplot2)
library(stringr)
library(nnet)
library(e1071)
library(DMwR)
library(mltools)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(caret)
library(ggcorrplot)
```

#Read and Import Data
```{r}
data <- read.csv("ALL_COUNTRIES.csv")
data
```

#Preview the Dataset
```{r}
set.seed(100)
data <- data[sample(nrow(data), 2500),]
data <- data[,c(2,7,10)]
data
head(data)
summary(data)
dim(data)
str(data)

data1 <- data
```

#check for missing data
```{r}
colSums(is.na(data))
```

#convert categorical variables
```{r}
data$show_type <- as.numeric(as.factor(data$show_type))
data$is_NF_Ori <- as.numeric(as.factor(data$is_NF_Ori))
str(data)
```

#split into training and testing set 
```{r}
nrow(data)
rows <- c(1:nrow(data))
split <- sample(rows,size = (nrow(data)*0.80))
train1 <- as.data.frame(data[split,])
test1 <- as.data.frame(data[-split,])
nrow(train1)
head(train1)
nrow(test1)
head(test1)
```

#create linear regression model 
```{r}
lr <- lm(imdb_rating ~ ., data = train1)
summary(lr)
plot(lr$residuals, pch = 16, col = "blue") #Plot the results
```

#validate the linear regression model
```{r}
train.control <- trainControl(method = "cv", number = 5)
model <- train(imdb_rating ~ ., data = train1, method = "lm", trControl = train.control)
print(model)
```

#predict on lr 
```{r}
pred <- predict(lr, data.frame(test1))

#error
paste( "RMSE =",RMSE(test1$imdb_rating, pred))

#residuals
Residuals <- test1$imdb_rating - pred
data.frame("Predicted" = pred, "Actual" = test1$imdb_rating,"Residual" = Residuals )
hist(Residuals, breaks = 25, xlab = "Residuals", main = "")

```

#Print first row
```{r}
newtest<- test1[1,1:3]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(data$show_type))){
  for (j in 1:as.numeric(max(data$is_NF_Ori))){
      newtest[nrow(newtest) + 1,] = list(q,j)
  }
}
```

#predict and order results in descending order
```{r}
pred <- predict(lr, data.frame(newtest[,1:2]))
pred<-as.data.frame(pred)
a<-data.frame(newtest[,1:2],pred$pred)
a
qw <- a[order(a$pred.pred,decreasing = TRUE),][-1,]
qw
```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  STnum <- as.numeric(row$show_type[1])
  NOnum <- as.numeric(row$is_NF_Ori[1])

  #look in show type in factored movie data table
  #store the index number
  #look back at genre 1 in original data table
  #print out character genre for that index
  index<-data[which(data[,"show_type"]==STnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  STLabel <- data1[index,1]
  
  #look in genre 2 in factored movie data table
  index<-data[which(data[,"is_NF_Ori"]==NOnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  NOLabel <- data1[index,2]
  
  #returns three genres into a list
  return <- list(STLabel,NOLabel)
}
```

#Top 3 combinations of movie genres
```{r}
topLabels<- test1[1,1:2]

for (i in 1:3){
  labels<- getStringGenres(qw[i,])
  topLabels[nrow(topLabels) + 1,] = labels
}
#top 3 
topLabels[-1,]
```