---
title: "NN_GENRE"
author: "Whitney Chu"
date: "04/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import libraries
```{r}
library(datasets)
library(neuralnet)
library(caret)
library(reshape2)
library(ggplot2)
library(stringr)
library(nnet)
library(e1071)
library(DMwR)
library(mltools)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(caret)
library(ggcorrplot)
```

#Read and Import Data
```{r}
movie.data <- read.csv("IMDb_movies.csv")
movie.data
```

#Preview the Dataset
```{r}
set.seed(100)
movie.data <- movie.data[,c(6:8,14)]
movie.data <- movie.data[sample(nrow(movie.data), 2500),]
movie.data <- as.data.frame(movie.data)
head(movie.data)
summary(movie.data)
dim(movie.data)
str(movie.data)


movie.data1 <- movie.data
```

#Check for missing data
```{r}
colSums(is.na(movie.data))
```

#Convert categorical variables
```{r}
movie.data$genre1 <- as.numeric(as.factor(movie.data$genre1))
movie.data$genre2 <- as.numeric(as.factor(movie.data$genre2))
movie.data$genre3 <- as.numeric(as.factor(movie.data$genre3))
summary(movie.data)
```

#Correlation matrix
```{r}
movie.rating <- (movie.data)
corr <- cor(movie.rating)
ggcorrplot(corr)
corr <- as.table(corr)
```

#Split data into training and testing set 
```{r}
nrow(movie.data)
rows <- c(1:nrow(movie.data))
split <- sample(rows,size = (nrow(movie.data)*0.80))
train1 <- as.data.frame(movie.data[split,])
test1 <- as.data.frame(movie.data[-split,])
nrow(train1)
head(train1)
nrow(test1)
head(test1)
```

#Create neural network model 
```{r}
nn <- neuralnet(avg_vote ~ genre1 + genre2 + genre3, data = train1, hidden = c(6), stepmax = 1e6)
nn$result.matrix
plot(nn)
```

#Validate the neural netowrk model
```{r}
train1
folds <- createFolds(train1$avg_vote, k = 5)
str(folds)
results <- c()
for (fld in folds){
  index <- sample(1:nrow(train1),round(0.8*nrow(train1)))
  data <- train1[-fld,]
  nn <- neuralnet(avg_vote ~ ., data = train1, hidden = c(4))
  pred.val1 <- compute(nn, train1[,1:3])
  results <- cbind(results,RMSE(pred.val1$net.result, train1$avg_vote))
}
paste("After", length(results), "validation loops the root mean squared error of the network is", paste0(round(mean(results),2)))
```


#Predict on NN and Error
```{r}
#predict
pred <- compute(nn, test1[,1:3])
results.test <- data.frame(actual = test1$avg_vote, prediction = pred$net.result)
results.test

#error
paste( "RMSE =", RMSE(pred$net.result, test1$avg_vote))

#highest predicted rating
paste("Highest predicted rating =", round(max(pred$net.result), digits = 1))
```

#Plot accuracy
```{r}
plot(results.test, col='blue', pch=16, main = "predicted vs actual for the testing set", ylab = "predicted", xlab = "actual")
```
#Print first row
```{r}
newtest<- test1[1,1:3]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(movie.data$genre1))){
  for (j in 1:as.numeric(max(movie.data$genre2))){
    for (x in 1:as.numeric(max(movie.data$genre3))){
      newtest[nrow(newtest) + 1,] = list(q,j,x)
    }
  }
}
```

#predict and order results in descending order
```{r}
pred <- compute(nn, newtest[,1:3])
pred
a<-data.frame(newtest[,1:3],pred$net.result)
a
qw<- a[order(a$pred.net.result,decreasing = TRUE),][-1,]
qw
```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  g1num <- as.numeric(row$genre1[1])
  g2num <- as.numeric(row$genre2[1])
  g3num <- as.numeric(row$genre3[1])
  
  #look in genre 1 in factored movie data table
  #store the index number
  #look back at genre 1 in original data table
  #print out character genre for that index
  index<-movie.data[which(movie.data[,"genre1"]==g1num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g1Label <- movie.data1[index,1]
  
  #look in genre 2 in factored movie data table
  index<-movie.data[which(movie.data[,"genre2"]==g2num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g2Label <- movie.data1[index,2]
  
  #look in genre 3 in factored movie data table
  index<-movie.data[which(movie.data[,"genre3"]==g3num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g3Label <- movie.data1[index,3]
  
  #returns three genres into a list
  return <- list(g1Label,g2Label,g3Label)
}
```

#Top 10 combinations of movie genres
```{r}
topLabels<- test1[1,1:3]

for (i in 1:20){
  labels<- getStringGenres(qw[i,])
  topLabels[nrow(topLabels) + 1,] = labels
}
#top 10 
topLabels[-1,]
```

