---
title: "NN_NETSHOW"
author: "Whitney Chu"
date: "22/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import libraries
```{r}
library(datasets)
library(neuralnet)
library(caret)
library(reshape2)
library(ggplot2)
library(stringr)
library(nnet)
library(e1071)
library(DMwR)
library(mltools)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(caret)
library(ggcorrplot)
```

#Read and Import Data
```{r}
data <- read.csv("ALL_COUNTRIES.csv")
data
```

#Preview the Dataset
```{r}
set.seed(100)
data <- data[sample(nrow(data), 2500),]
data <- data[,c(2,7,10)]
data
head(data)
summary(data)
dim(data)
str(data)

data1 <- data
```

#check for missing data
```{r}
colSums(is.na(data))
```

#convert categorical variables
```{r}
data$show_type <- as.numeric(as.factor(data$show_type))
data$is_NF_Ori <- as.numeric(as.factor(data$is_NF_Ori))
str(data)
```
#Correlation matrix
```{r}
rating <- (data)
corr <- cor(rating)
ggcorrplot(corr)
corr <- as.table(corr)
```

#split into training and testing set 
```{r}
nrow(data)
rows <- c(1:nrow(data))
split <- sample(rows,size = (nrow(data)*0.80))
train1 <- as.data.frame(data[split,])
test1 <- as.data.frame(data[-split,])
nrow(train1)
head(train1)
nrow(test1)
head(test1)
```

#create neural network model 
```{r}
  nn <- neuralnet(imdb_rating ~ ., data = train1, hidden = c(6), stepmax = 1e6)
nn$result.matrix
plot(nn)
```


#validate the neural network model 
```{r}
folds <- createFolds(train1$imdb_rating, k = 5)
str(folds)
results <- c()
for (fld in folds){
  index <- sample(1:nrow(train1),round(0.8*nrow(train1)))
  data <- train1[-fld,]
  nn <- neuralnet(imdb_rating ~ show_type + is_NF_Ori, data = train1, hidden = c(4))
  pred.val <- compute(nn, train1[,1:2])
  results <- cbind(results,RMSE(pred.val$net.result, train1$imdb_rating))
}
paste("After", length(results), "validation loops the root mean squared error of the network is", paste0(round(mean(results),2)))
```

#predict on NN 
```{r}
pred <- compute(nn, test1[,1:2])
results.test <- data.frame(actual = test1$imdb_rating, prediction = pred$net.result)
results.test

#error
paste( "RMSE =", RMSE(pred$net.result, test1$imdb_rating))

#highest predicted rating
paste("Highest predicted rating =", round(max(pred$net.result), digits = 2))
```

#plot accuracy
```{r}
#scaled
plot(results.test, col='blue', pch=16, main = "predicted vs actual for the testing set", ylab = "predicted", xlab = "actual")
```

#Print first row
```{r}
newtest<- test1[1,1:2]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(data$show_type))){
  for (j in 1:as.numeric(max(data$is_NF_Ori))){
      #print(q,j)
      newtest[nrow(newtest) + 1,] = list(q,j)
  }
}
newtest<-newtest[-1,]
newtest
```

#predict and order results in descending order
```{r}
pred <- compute(nn, newtest[,1:2])
a<-data.frame(newtest[,1:2],pred$net.result)
a
a[order(a$pred.net.result,decreasing = TRUE),]
```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  STnum <- as.numeric(row$show_type[1])
  NOnum <- as.numeric(row$is_NF_Ori[1])
  
  #look in show type in factored movie data table
  #store the index number
  #look back at show type in original data table
  #print out character genre for that index
  index<-data[which(data[,"show_type"]==STnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  STLabel <- data1[index,1]
  
  #look in is_NF_Ori in factored movie data table
  index<-data[which(data[,"is_NF_Ori"]==NOnum),][1,0]
  index<-toString(as.numeric(row.names((index))))
  NOLabel <- data1[index,2]
  
  
  
  #returns three genres into a list
  return <- list(STLabel,NOLabel)
}
```

#Top 3 combinations of movie genres
```{r}
topLabels<- test1[1,1:2]
topLabels
for (i in 1:3){
  labels<- getStringGenres(a[order(a$pred.net.result,decreasing = TRUE),][i,])
  topLabels[nrow(topLabels) + 1,] = labels
  if(i==1){
    topLabels<-topLabels[-1,]
  }
}
#top 3 
topLabels
```