---
title: "SVM_Genres_MOVIEPROJECT"
author: "Whitney Chu"
date: "04/11/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import libraries
```{r}
library(forecast)
library(tidyverse)    
library(e1071)  
library(RColorBrewer)
library(dplyr)
library(caTools)
library(datasets)
library(neuralnet)
library(caret)
library(reshape2)
library(ggplot2)
library(stringr)
library(nnet)
library(DMwR)
library(mltools)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(ggcorrplot)
library(randomForest)
```

#Read and Import Data
```{r}
movie.data <- read.csv("IMDb_movies.csv")
movie.data
```

#Preview the Dataset
```{r}
set.seed(100)
movie.data <- movie.data[sample(nrow(movie.data), 2500),]
movie.data <- movie.data[,c(6:8,14)]
movie.data
head(movie.data)
summary(movie.data)
dim(movie.data)
str(movie.data)

movie.data1 <- movie.data
```

#check for missing data
```{r}
colSums(is.na(movie.data))
```

# Adding binary, dependent variable for svm analysis
```{r}
movie.data$FavourableMovie <- ifelse(movie.data$avg_vote>=6.4,1,0)
str(movie.data)
View(movie.data)
```

#convert categorical variables
```{r}
movie.data$genre1 <- as.numeric(as.factor(movie.data$genre1))
movie.data$genre2 <- as.numeric(as.factor(movie.data$genre2))
movie.data$genre3 <- as.numeric(as.factor(movie.data$genre3))
movie.data
```

#Correlation matrix
```{r}
movie.rating <- (movie.data)
corr <- cor(movie.rating)
ggcorrplot(corr)
corr <- as.table(corr)
```

#split into training and testing set 
```{r}
#set.seed(100)
nrow(movie.data)
rows <- c(1:nrow(movie.data))
split <- sample(rows,size = (nrow(movie.data)*0.80))
train <- movie.data[split,]
test <- (movie.data[-split,])

nrow(train)
head(train)
str(train)
nrow(test)
head(test)
```

#create SVM model 
```{r}
Moviesvm <- svm(formula = FavourableMovie ~ genre1 + genre2 + genre3, data = train, kernel = 'linear')
summary(Moviesvm)
```

#Cross-validation of Cost
```{r}
tune.out <- tune(svm ,FavourableMovie~ genre1 + genre2 + genre3,data=train ,kernel ="linear",cross = 5, ranges =list(cost=c(0.001,0.01,0.1, 1.5, 10)))
summary(tune.out)
bestmod =tune.out$best.model
print(bestmod)
optimal_cost <- bestmod$cost
```

#svm model with optimal cost
```{r}
Moviesvm <- svm(formula = FavourableMovie ~ genre1 + genre2 + genre3, data = train, cost = optimal_cost, kernel = 'linear')
summary(Moviesvm)
```

#prediction and error
```{r}
pred.svm <- predict(Moviesvm,test)
pred <- ifelse(pred.svm >=0.64, "1", "0")
mean(test$FavourableMovie!=pred)
table(pred, test$FavourableMovie)
```

#ROC curve
```{r}
plot(roc(test$FavourableMovie, pred.svm, direction="<"),
     col="yellow", lwd=3, main="ROC curve")
```

#Print first row
```{r}
newtest<- test[1,1:3]
newtest
```

#Iterate all the possibilites
```{r}
for (q in 1:as.numeric(max(movie.data$genre1))){
  for (j in 1:as.numeric(max(movie.data$genre2))){
    for (x in 1:as.numeric(max(movie.data$genre3))){
      newtest[nrow(newtest) + 1,] = list(q,j,x)
    }
  }
}
```

#predict and order results in descending order
```{r}
predict.ret <- predict(Moviesvm,newtest[,1:3])
predict.ret <- as.data.frame(predict.ret)
predict.ret1 <- predict.ret

#binary result - inconclusive
pred <- ifelse(predict.ret >=0.64, "1", "0")
a <- data.frame(newtest[,1:3],pred)
a
qw <- a[order(a$predict.ret,decreasing = TRUE),][-1,]
qw

#without making prediction binary
a2 <- data.frame(newtest[,1:3],predict.ret1)
a2
qw2 <- a2[order(a2$predict.ret,decreasing = TRUE),][-1,]
qw2

```

#convert factors back to characters
```{r}
getStringGenres <- function(row) {
  #make genres numeric
  g1num <- as.numeric(row$genre1[1])
  g2num <- as.numeric(row$genre2[1])
  g3num <- as.numeric(row$genre3[1])
  
  #look in genre 1 in factored movie data table
  #store the index number
  #look back at genre 1 in original data table
  #print out character genre for that index
    index<-movie.data[which(movie.data[,"genre1"]==g1num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g1Label <- movie.data1[index,1]
  
  #look in genre 2 in factored movie data table
  index<-movie.data[which(movie.data[,"genre2"]==g2num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g2Label <- movie.data1[index,2]
  
  #look in genre 3 in factored movie data table
  index<-movie.data[which(movie.data[,"genre3"]==g3num),][1,0]
  index<-toString(as.numeric(row.names((index))))
  g3Label <- movie.data1[index,3]
  
  #returns three genres into a list
  return <- list(g1Label,g2Label,g3Label)
}
```

#Top 10 combinations of movie genres
```{r}
topLabels<- test[1,1:3]

for (i in 1:10){
  labels <- getStringGenres(qw2[i,])
  topLabels[nrow(topLabels) + 1,] = labels
}
#top 10 
topLabels[-1,]
```